Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-04 docs/ms.tex
Update ms.tex

We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
sets as described in section 4.1 .Each data set has 64 patches and 8$\times$64 galaxies,and
the true P($\epsilon$) is Beta(2.8,2.8).The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 
64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 . 
with prior prefator $\xi=3$.The results of the systematical bias
analysis are tabulated in table 1.

>>>>

We calculated the average of $g^{estimated}-g^{true}$ of 10,000 data
sets as described in section 4.1 .Each data set has 64 patches and 8$\times$64 galaxies,and
the true P($\epsilon$) is Beta(2.8,2.8).The step function model is used with the prior prefator $\xi=3$.
The input true values of $\vec{g}_{1}$ and $\vec{g}_{2}$ of the 64$\times$10,000 sky patches are generated randomly from a uniform distribution from -0.1 to 0.1 . 
The results of the systematical bias analysis are tabulated in table 1.
